---
title: "Analysing the PublicHouse dataset"
author: "James Gleeson"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.caption = FALSE, fig.retina = 2, dev.args = list(png = list(type = "cairo")))
```

## Introduction

The [PublicHouse dataset](https://github.com/jgleeson/PublicHouse) is a compilation of publicly available data on the number of dwellings and people in cities and countries around the world. The [README](https://github.com/jgleeson/PublicHouse/blob/main/README.md) provides details about the creation of the dataset, while this note sets out some basic analysis. It also includes the R code used to carry out the analysis, so you can re-create or adapt the charts.

Let's start by loading the R packages we're going to use. We're not going to be doing anything very complicated so we can mainly use the [tidyverse](https://www.tidyverse.org/) family of packages.

```{r load libraries}
library(tidyverse)
library(khroma) # for the Okabe-Ito colour scale
library(lubridate)
```

Another bit of setup is to set some ggplot defaults.

```{r set theme}
theme_set(theme_minimal(base_size = 14))
theme_update(text = element_text(family = "Calibri"), 
             plot.title = element_text(size = 12, hjust = 0.5)) 
```

## Loading and examining the data

Now we load the dataset straight from Github. 

```{r load data}
d <- read_csv("https://raw.githubusercontent.com/jgleeson/PublicHouse/main/dataset.csv") %>%
  mutate(ref_date = dmy(ref_date))
```

As a first step, let's see what places and years we have data for. PublicHouse includes data on both cities and countries, so let's start with countries. Each dot is an observation. 

```{r coverage plot for countries, fig.height= 6.5, fig.width = 9}
d %>%
  filter(area_level != "city-region") %>%
  mutate(variable = str_to_title(variable)) %>%
  ggplot(aes(x = year, y = variable, colour = variable)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.5) +
  scale_colour_okabeito() +
  labs(x = NULL, y = NULL,
       title = "PublicHouse data coverage by country") +
  facet_wrap(~area_name) +
  theme(legend.position = "none",
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))
```

And here's the same thing but for cities. The coverage is not as good for cities as for countries, with fewer places and points in time covered. Sometimes this is because there simply isn't any sub-national data reported, but often it's because there is sub-national data but not at a city level. Note, they're not included in the chart below but I have labelled Singapore and Hong Kong as 'city states' and included them in both the country and city charts in the rest of the document.

```{r coverage plot for cities, fig.height= 6, fig.width = 9}
d %>%
  filter(area_level == "city-region") %>%
  mutate(variable = str_to_title(variable)) %>%
  ggplot(aes(x = year, y = variable, colour = variable)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.5) +
  scale_colour_okabeito() +
  labs(x = NULL, y = NULL,
       title = "PublicHouse data coverage by city") +
  facet_wrap(~area_name) +
  theme(legend.position = "none",
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))
```

## Dwellings per person

A good place to start is by looking at how much housing there is to go around in each country or city. But it wouldn't make much sense to just measure the number of dwellings, so instead we calculate a measure of dwellings per person (or dwellings per 1,000 people in the charts below, for presentation purposes). This measures the stock of housing, scaled to the population of the area. The inverse of dwellings per person is persons per dwelling, which is similar to the average household size - but household size is affected by vacancy, second homes and sharing so is harder to measure. 

Is a higher rate of dwellings per person a good thing? Well, housing is a 'normal' good in the sense that people generally demand more of it as their incomes increase, so within a given place we would expect to see an increase over time. 

The chart below shows the trend in dwellings per 1,000 people over time for countries, colour-coded by a country grouping of my own devising (which is inevitably slightly arbitrary - I've put France (and Paris) in the 'Southern Europe' category, for example). Note, the x axis starts at 1980 as there are relatively few countries with data before that, and the y axis starts at 200. 

```{r dwellings per person trend by country, fig.height = 7, fig.width=9}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = dpp, group = area_name, colour = grouping)) +
  geom_line(size = 0.75) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  scale_y_continuous(limits = c(200, 650)) + 
  labs(x = NULL, y = NULL, title = "Dwellings per 1,000 people by country") +
  facet_wrap(~area_name) +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))

```

A couple of patterns stand out here. First, there is a lot of variation in both the level of dwellings per person and the rate of growth over time. Second, in many countries there is a flattening of the curve in roughtly the second half of the period (since 2000), Spain and Ireland being quite extreme examples. Third, East Asian and Southern European countries have generally seen bigger increases over time, while Anglophone countries haven't seen much increase at all since 2000.

Next is the trend over time for cities. There are two things to note: first, that the level of dwellings per person is generally higher in cities than for countries, even though dwellings and households are typically smaller in urban areas. The second is that the slope of the lines for cities are more often horizontal or downwards, reflecting the resurgence in population growth in many cities and the failure to increase urban housing stocks fast enough.

```{r dwellings per person trend by city, fig.height = 7, fig.width=9}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "country") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = dpp, group = area_name, colour = grouping)) +
  geom_line(size = .75) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  scale_y_continuous(limits = c(200, 650)) + 
  labs(x = NULL, y = NULL, title = "Dwellings per 1,000 people by city") +
  facet_wrap(~area_name) +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))

```

```{r dpp latest year, fig.height= 4.5, fig.width=5, include = F}
# This chart shows a comparison between the latest year and a decade before (where data is available), for cities.
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
        names_from = variable,
        values_from = value) %>%
  mutate(dpp = dwellings/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "country") %>%
  group_by(area_name) %>%
  filter(max(year) > 2017) %>%
  filter(year == max(year) | (year == max(year)-10)) %>% 
  arrange(dpp) %>%
  ggplot(aes(x = reorder(area_name,dpp), y = dpp*1000, fill = year)) +
  geom_point(size = 4.5, shape = 21, colour = "white",
             alpha = 0.7) +
  coord_flip() +
  labs(x = NULL, y = NULL, title = "Dwellings per 1,000 people by city in most recent year \nand 10 years earlier (where available)") +
  theme(panel.grid.major.x = element_line(colour = "grey80"),
        panel.grid.major.y = element_line(colour = "grey90"),
        legend.position = "bottom")
```

Here's another way of looking at the same data - taking the most recent year's figure for dwellings per 1,000 people (as long as there is one more recently than 2015) and calculating the percentage change from a decade earlier. The chart combines countries (in bold font) and cities, again coloured according to country grouping. The vertical dark line divides places where dwellings per person increased (to the right) from places where it fell (to the left). The horizontal dark line divides places with higher than average dwellings per person (above the line) from places with lower than the average (below the line).

```{r dpp level and change scatter, fig.height= 7, fig.width=8}
scatter_data <- d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
        names_from = variable,
        values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  group_by(area_name) %>%
  filter(max(year) > 2015) %>%
  filter(year == max(year) | (year == max(year)-10)) %>% 
  mutate(dpp_change = dpp/dpp[1]-1) %>%
  filter(dpp_change !=0) %>%
  ungroup()

dpp_average <- scatter_data %>% summarise(mean(dpp)) %>% as.double()

scatter_data %>%
  mutate(face = case_when(
    area_level != "city-region" ~ "bold",
    TRUE ~ "italic"
  )) %>%
  ggplot(aes(x = dpp_change, y = dpp, colour = grouping)) +
  geom_text(aes(label = area_name, fontface = face), size = 3) +
  geom_hline(yintercept = dpp_average) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(limits = c(NA, 650)) +
  labs(x = "% change in 10 years", y = "Dwellings per person, latest year", title = "Dwellings per 1,000 people and change over 10 years (where available)", caption = "City names in italics, countries in bold") +
  scale_colour_okabeito() +
  theme(panel.grid.major.x = element_line(colour = "grey80"),
        panel.grid.major.y = element_line(colour = "grey90"),
        legend.position = "bottom",
        legend.title = element_blank())
```

There are some quite striking patterns here. First, all of the Anglophone places have fewer dwellings per person than the average, and around half of them have also seen declines over the last decade. Southern European places almost all have more dwellings per person than average and have seen increases (Madrid and Barcelona being the notable exceptions). East Asian places have very different amounts of housing per person, but all saw significant increases over the period (particularly Singapore).

But it's important to remember that the number of dwellings per person can change due to shifts in population as well as net housing supply. The following two charts separate out the contribution of changes in population and changes in the housing stock.

```{r dpp change decomposition - countries, fig.width = 8, fig.height= 5}
d %>%
  filter(area_level != "city-region") %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
        names_from = variable,
        values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  group_by(area_name) %>%
  filter(max(year) > 2015) %>%
  filter(year == max(year) | (year == max(year)-10)) %>% 
  mutate(dpp_change = dpp - dpp[1],
         dpp_constant_pop = dwellings*1000/population[1],
         "Contribution of dwelling change" = dpp_constant_pop-dpp[1],
         dpp_constant_dwellings = dwellings[1]*1000/population,
         "Contribution of population change" = dpp_constant_dwellings-dpp[1]) %>% 
  filter(dpp_change != 0) %>%
  select(-c(dwellings, population, dpp, dpp_constant_pop, dpp_constant_dwellings)) %>% 
  rename("Change in dwellings per 1,000 people" = dpp_change) %>%
  pivot_longer(-c(area_name, year, area_level, grouping), names_to = "variable", values_to = "value") %>%
  ungroup() %>%
  ggplot(aes(x = area_name, y = value, fill = variable)) +
  geom_col(data = . %>% filter(variable != "Change in dwellings per 1,000 people")) +
  geom_point(data = . %>% filter(variable == "Change in dwellings per 1,000 people"),
             shape = 21, size = 2) +
  coord_flip() +
  scale_fill_okabeito() +
  labs(x = NULL, y = NULL, title = "Contribution of population and housing stock changes to change in dwellings per 1,000 people") +
  facet_grid(grouping ~ ., scales = "free_y", space = "free_y") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.width = unit(8, "pt"),
        strip.text.y = element_text(angle = 0),
        strip.background = element_rect(fill = "grey80", colour = "grey80"),
        panel.spacing.y = unit(10, "pt")) 
```

At the country level, we can see that only three countries (Poland, Japan and Portugal) saw a fall in their populations over the decade, contribution to an increase in dwellings per person. And unsurprisingly, no countries saw a decrease in their housing stock. Population growth was highest in the Anglophone countries, which contrbuted to their low or negative growth in dwellings per person. East Asian countries had low population growth but still added a significant number of new homes.

```{r dpp change decomposition - cities, fig.width = 8, fig.height= 5}
d %>%
  filter(area_level != "country") %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
        names_from = variable,
        values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  group_by(area_name) %>%
  filter(max(year) > 2015) %>%
  filter(year == max(year) | (year == max(year)-10)) %>% 
  mutate(dpp_change = dpp - dpp[1],
         dpp_constant_pop = dwellings*1000/population[1],
         "Contribution of dwelling change" = dpp_constant_pop-dpp[1],
         dpp_constant_dwellings = dwellings[1]*1000/population,
         "Contribution of population change" = dpp_constant_dwellings-dpp[1]) %>% 
  filter(dpp_change != 0) %>%
  select(-c(dwellings, population, dpp, dpp_constant_pop, dpp_constant_dwellings)) %>% 
  rename("Change in dwellings per 1,000 people" = dpp_change) %>%
  pivot_longer(-c(area_name, year, area_level, grouping), names_to = "variable", values_to = "value") %>%
  ungroup() %>%
  ggplot(aes(x = area_name, y = value, fill = variable)) +
  geom_col(data = . %>% filter(variable != "Change in dwellings per 1,000 people")) +
  geom_point(data = . %>% filter(variable == "Change in dwellings per 1,000 people"),
             shape = 21, size = 2) +
  coord_flip() +
  scale_fill_okabeito() +
  labs(x = NULL, y = NULL, title = "Contribution of population and housing stock changes to change in dwellings per 1,000 people") +
  facet_grid(grouping ~ ., scales = "free_y", space = "free_y") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.width = unit(8, "pt"),
        strip.text.y = element_text(angle = 0),
        strip.background = element_rect(fill = "grey80", colour = "grey80")) 
```

At the city level, there were no cases of shrinking populations. The fastest growth in urban populations was generally in the Central/Northern European cities, and the lowest in Southern European cities (including Paris). Only in East Asia did cities consistently manage to grow their housing stock faster than their population.

The next chart plots all the country-level data on one chart and derives an overall average trend for each country grouping. These average trends are more representative for some groupings than for others: for example, the East Asian group is quite small and very diverse, with huge differences in trends between, say, Singapore and Japan. The other key point to note about these average trend lines is that they aren't weighted for the population size of each country - so in the Anglophone grouping, for example, the data for the USA has no more effect on the trend than the data for Ireland.

With those caveats, this chart does reveal some striking general patterns. In particular, there has on average been no increase in the amount of housing per person in the Anglophone countries since the start of the 1980s, while there has been a significant (but slowing) increase in Southern Europe, and increases over time (though quite unsteady after 2000) in Central/Northern Europe and East Asia.

```{r aggregate dwellings per person trend by country, fig.height = 5, fig.width= 7}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = dpp, colour = grouping)) +
  geom_point(alpha = 0.1, size = 3) +
  geom_smooth(se = F, span = 0.3) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  coord_cartesian(ylim = c(200, 650)) + 
  labs(x = NULL, y = NULL, title = "Dwellings per 1,000 people by country grouping") +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey80"))

```

Finally, this chart shows an overall average trend for every country, and compares that to the England trend. Broadly speaking, England started out with more housing per person than the international average, but has ended up with less.

```{r dwellings per person trend by country with England focus, fig.height = 4, fig.width = 6}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  mutate(dpp = dwellings*1000/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1959) %>%
  ggplot() +
  geom_smooth(aes(x = year, y = dpp, colour = "International average trend"), span = 0.4) +
  geom_line(data = . %>% filter(area_name == "England"), 
            aes(x = year, y = dpp, colour = "England")) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1960, 1980, 2000, 2020)) +
  labs(x = NULL, y = NULL, title = "Dwellings per 1,000 people - England and aggregate international trends") +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

## Net additional dwellings per 1,000 population

There are a number of other measures of housing stock or supply you could use, but this section focuses on the net annualised change in dwellings per 1,000 population. Whereas dwellings per (1,000) people is a measure of *stock*, this is a measure of *flow*, and it is not affected by either the previous size of the stock or by the change in population (at least not very much). So countries that are building a lot of homes relative to their population can 'look good' by this measure even if that new supply isn't actually enough to keep up with population growth. 

The first chart in this section shows this measure for countries. The trend in most countries actually looks fairly flat by this measure, largely because of some extremely high values in a few countries (notably Ireland and South Korea) 

```{r annualised net dwellings per capita by country, fig.width = 9, fig.height = 6.5}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  group_by(area_name) %>%
  mutate(net_change = (dwellings - lag(dwellings, 1))/(year - lag(year, 1)),
         net_change_per_1k = net_change/((population + lag(population, 1))/2)*1000) %>%
  filter(!is.na(net_change_per_1k)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = net_change_per_1k, group = area_name, colour = grouping)) +
  geom_line(size = 0.75) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  labs(x = NULL, y = NULL, title = "Annualised net additional dwellings per 1,000 people by country") +
  facet_wrap(~area_name) +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))
```

Here's the same chart for cities. Again the extreme outliers (hello Seoul!) tend to flatten the trend for everywhere else. The breaks in the trends for Berlin and Brussels are due to the net dwelling change briefly going negative - I suspect due to data collection reasons rather than an actual shrinkage of the housing stock.

```{r net dwellings per capita by city, fig.height = 6.5, fig.width = 9}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  group_by(area_name) %>%
  mutate(net_change = (dwellings - lag(dwellings, 1))/(year - lag(year, 1)),
         net_change_per_1k = net_change/((population + lag(population, 1))/2)*1000) %>%
  filter(!is.na(net_change_per_1k)) %>%
  filter(area_level != "country") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = net_change_per_1k, group = area_name, colour = grouping)) +
  geom_line(size = 0.75) +
  scale_colour_okabeito() +
  scale_y_continuous(limits = c(0, NA)) +
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  labs(x = NULL, y = NULL, title = "Annualised net additional dwellings per 1,000 people by city") +
  facet_wrap(~area_name) +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        strip.background = element_rect(colour = "grey80", fill = "grey80"),
        panel.border = element_rect(colour = "grey80", fill = NA),
        panel.spacing.x = unit(15, units = "pt"))
```

Can we extract any aggregate trends? The chart below shows smoothed averages for country groupings, but as the quite widely dispersed dots around each trend should suggest, these are fairly indicative trends at best. Broadly speaking it looks like new supply peaked in East Asian around 2000 (possibly as a result of the late 1990s financial crisis in that region), while there was a peak in supply around the time of the global financial crisis in Anglophone countries and (a much stronger effect) in Southern European countries. The European and (in particular) the Anglophone countries have increased supply in recent years while in East Asia supply has fallen.

```{r summary net additions chart by country, fig.height = 5, fig.width=6}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  group_by(area_name) %>%
  mutate(net_change = (dwellings - lag(dwellings, 1))/(year - lag(year, 1)),
         net_change_per_1k = net_change/((population + lag(population, 1))/2)*1000) %>%
  filter(!is.na(net_change_per_1k)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1979) %>%
  ggplot(aes(x = year, y = net_change_per_1k, colour = grouping)) +
  geom_point(alpha = 0.1, size = 3) +
  geom_smooth(se = FALSE, span = 0.4) +
  scale_colour_okabeito() +
  coord_cartesian(ylim = c(0, 10)) + # use this rather than scale_x_continuous to 'zoom' into a section of the chart without losing any data 
  scale_x_continuous(breaks = c(1980, 2000, 2020)) +
  labs(x = NULL, y = NULL, title = "Annualised net additional dwellings per 1,000 people by country") +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey80"))
```

And finally, here's the aggregate trend for all countries compared to England. The long-term international trend is downwards, though there are fairly few observations in the early years of the dataset. Except for one brief point in the late 1980s, England has had lower net housing supply per person than the international trend throughout this period.

```{r summary net additions chart with England focus, fig.height = 4.5, fig.width=6}
d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  group_by(area_name) %>%
  mutate(net_change = (dwellings - lag(dwellings, 1))/(year - lag(year, 1)),
         net_change_per_1k = net_change/((population + lag(population, 1))/2)*1000) %>%
  filter(!is.na(net_change_per_1k)) %>%
  filter(area_level != "city-region") %>% 
  filter(year > 1959) %>%
  ggplot() +
  geom_smooth(aes(x = year, y = net_change_per_1k, 
                  colour = "International average trend"), span = 0.4) +
  geom_line(data = . %>% filter(area_name == "England"),
            aes(x = year, y = net_change_per_1k, colour = "England")) +
  scale_colour_okabeito() +
  scale_x_continuous(breaks = c(1960, 1980, 2000, 2020)) +
  labs(x = NULL, y = NULL, title = "Annualised net additional dwellings per 1,000 people - \nEngland and aggregate international trends") +
  theme(legend.position = "bottom",
        legend.title = element_blank(), 
        panel.grid.major.y = element_line(colour = "grey80"))


```
There is lots more that can be done with this dataset, and I encourage you to try your own analysis. Hopefully the coverage will also expand over time - on which point, please see the [README](https://github.com/jgleeson/PublicHouse/blob/main/README.md) for details of how to contribute.
