---
title: "Analysing the Openhouse dataset"
author: "James Gleeson"
date: "November 2021"
output: github_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

The [Openhouse dataset](https://github.com/jgleeson/openhouse) is a compilation of publicly available data on the number of dwellings and people in cities and countries around the world. The [README](https://github.com/jgleeson/openhouse/blob/main/README.md) provides details about the creation of the dataset, while this note sets out some basic analysis.

Let's start by loading the R packages we're going to use. We're not going to be doing anything very complicated so we can mainly use the [tidyverse](https://www.tidyverse.org/) plus [ggthemes](https://yutannihilation.github.io/allYourFigureAreBelongToUs/ggthemes/) for styling.

```{r load libraries}
library(tidyverse)
library(ggthemes)
library(lubridate)
library(plotly)
```

Another bit of setup is to set the chart theme to use.

```{r set theme}
theme_set(theme_few())
```

## Loading and examining the data

Now let's load the data. 

```{r load data}
d <- read_csv("https://raw.githubusercontent.com/jgleeson/openhouse/main/dataset.csv") %>%
  mutate(ref_date = dmy(ref_date))
```

As a first step, let's see what places and dates we have data for. Openhouse includes data on both cities and countries, so let's start with countries. Each dot is an observation. 

```{r coverage plot for countries, fig.height= 5}
d %>%
  filter(area_level != "city-region") %>%
  ggplot(aes(x = year, y = variable, colour = variable)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.5) +
  labs(x = NULL, y = NULL) +
  facet_wrap(~area_name) +
  theme(legend.position = "none")
```

And here's the same thing but for cities.

```{r coverage plot for cities, fig.height= 5}
d %>%
  filter(area_level == "city-region") %>%
  ggplot(aes(x = year, y = variable, colour = variable)) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.5) +
  labs(x = NULL, y = NULL) +
  facet_wrap(~area_name) +
  theme(legend.position = "none")
```

## Dwellings per person

```{r dwellings per person}
static <- d %>%
  pivot_wider(id_cols = c(area_name, year, area_level, grouping),
              names_from = variable,
              values_from = value) %>%
  mutate(dpp = dwellings/population) %>%
  arrange(area_name, year) %>%
  filter(!is.na(dpp)) %>%
  filter(area_level != "city-region") %>% 
  ggplot(aes(x = year, y = dpp, group = area_name, colour = area_name)) +
#  geom_point() +
  geom_line() +
  labs(x = NULL, y = NULL, title = "Dwellings per person by country") +
  facet_wrap(~grouping) +
  theme()
static
```
That's a bit busy so let's see if we can do a plotly version

```{r create plotly}
dynamic <- ggplotly(static)
```
```{r include, echo = FALSE}
htmlwidgets::saveWidget(dynamic, "index.html")

htmltools::tags$iframe(
  src=file.path("index.html"),
  width="100%",
  height="600",
  scrolling="no",
  seamless="seamless",
  frameBorder="0"
)

```
